preparation

### 2025-03-07 fake_data/preparation_1.Rmd
Fake data: simulated data

```{r setup}
#install.packages("eeptools") 
#used for birthday -> age. Found out about this from a YouTube video
library(eeptools)
library(tidyverse)
```

@@

# Making relevant items numeric 
youtube <- youtube %>% 
  # malleable and behavior
  mutate(
    across(c(malleable_1, malleable_2, malleable_3, malleable_4, behavior_1, behavior_2, behavior_3, behavior_4, behavior_5, behavior_6, behavior_7),
           ~ recode(.,
             "Strongly disagree" = 1,
             "Somewhat disagree" = 2,
             "Neither agree nor disagree" = 3,
             "Somewhat agree" = 4,
             "Strongly agree" = 5
           ))) %>% 
  # homophily and parasocial 
  mutate(
    across(c(`homophily-appear_1`, `homophily-appear_2`, `homophily-appear_3`, `homophily-appear_4`, `homophily-appear_5`, `homophily-behave_1`, `homophily-behave_2`, `homophily-behave_3`, `homophily-behave_4`, `homophily-behave_6`, parasocial_1, parasocial_2, parasocial_3, parasocial_4, parasocial_5),
           ~ recode (.,
             "Really disagree" = 1,
             "Disagree" = 2,
             "I don't know" = 0,
             "Agree" = 3,
             "Really agree" = 4
           )))  %>% 
  # outgroup-freq
  mutate(`outgroup-freq` = recode(`outgroup-freq`, 
                "Never" = 1,
                "Rarely" = 2,
                "Sometimes" = 3,
                "Often" = 4,
                "Very often" = 5))
```

>>>>

```{r setup}
#install.packages("eeptools") 
#used for birthday -> age. Found out about this from a YouTube video
library(eeptools)
library(tidyverse)
install.packages("mediation")
library(mediation)
```

@@

# Making relevant items numeric 
youtube <- youtube %>% 
  # malleable and behavior
  mutate(
    across(c(malleable_1, malleable_2, malleable_3, malleable_4, behavior_1, behavior_2, behavior_3, behavior_4, behavior_5, behavior_6, behavior_7),
           ~ recode(.,
             "Strongly disagree" = 1,
             "Somewhat disagree" = 2,
             "Neither agree nor disagree" = 3,
             "Somewhat agree" = 4,
             "Strongly agree" = 5
           ))) %>% 
  # homophily and parasocial 
  mutate(
    across(c(`homophily-appear_1`, `homophily-appear_2`, `homophily-appear_3`, `homophily-appear_4`, `homophily-appear_5`, `homophily-behave_1`, `homophily-behave_2`, `homophily-behave_3`, `homophily-behave_4`, `homophily-behave_6`, parasocial_1, parasocial_2, parasocial_3, parasocial_4, parasocial_5),
           ~ recode (.,
             "Really disagree" = 1,
             "Disagree" = 2,
             "I don't know" = 3,
             "Agree" = 4,
             "Really agree" = 5
           )))  %>% 
  # outgroup-freq
  mutate(`outgroup-freq` = recode(`outgroup-freq`, 
                "Never" = 1,
                "Rarely" = 2,
                "Sometimes" = 3,
                "Often" = 4,
                "Very often" = 5))
```
